\documentclass{article}

% Preamble
\usepackage{amsmath,amssymb,amsthm}
\usepackage{hyperref}
\usepackage{booktabs}
\DeclareMathOperator{\DLap}{DLap}
\DeclareMathOperator{\MerkleRoot}{MerkleRoot}
\DeclareMathOperator{\Enc}{Enc}
\DeclareMathOperator{\Sign}{Sign}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{definition}{Definition}
\newtheorem{hypothesis}{Hypothesis}
\newtheorem{remark}{Remark}
\newtheorem{proposition}{Proposition}

\title{ANCRE v0.8: Privacy Guarantees Built\\
on Irreversible Destruction}

\author{Taha Houari\\
Independent Researcher, Paris, France\\
tahahouari@hotmail.fr\\
Preprint: HAL, May 2026}

\begin{document}
\maketitle

\begin{abstract}
Most privacy systems build guarantees on what
they protect. ANCRE builds its guarantees on
what it irrevocably destroys. We present ANCRE
v0.8, a role-separated aggregation protocol achieving
$\varepsilon=0.5$-DP for B2B audio analytics
under honest-majority assumption H6-MPC,
without trust in any single operator.
We prove that ANCRE is \emph{optimal}:
no privacy-destruction protocol can achieve
$\varepsilon$-DP with less noise under
substitute adjacency. The lower bound follows
from Le Cam's method applied to the
indistinguishability requirement.
\end{abstract}

% Section 1
\section{Introduction}
Radio platforms generate granular listening
signals carrying significant commercial value
for AI operators. Existing solutions require
trusting a single aggregation server.

ANCRE v0.7~\cite{houari2026ancre} addressed
this with central DP under honest-but-curious
H6. ANCRE v0.8 replaces H6 with H6-MPC:
breaking privacy requires collusion of
at least 2 of 3 independent parties.

\textbf{Contributions:}
\begin{itemize}
\item 3-party MPC protocol with threshold
      encryption and Merkle-anchored window closure
\item Formal H6-MPC replacing operational H6
\item $\varepsilon=0.5$-DP without single-server trust
\item \textbf{Optimality proof via Le Cam's method}
\item Publicly verifiable MPC attestation
\end{itemize}

% Section 2
\section{Parties and Roles}
\begin{itemize}
\item $P_1$: Collector (Radio France) ---
      receives encrypted signals, destroys raw data
\item $P_2$: DP Aggregator (VERA) ---
      holds decryption share, runs TMoM+DLap
\item $P_3$: Trusted Third Party (CNIL) ---
      validates timestamp, holds decryption share
\end{itemize}

% Section 3 — Protocol
% Section 3 inline

% Section 4 — Security
% Section 4 inline

% Section 5 — Lower Bound TCS
% Section 3 — Protocol
\input{section3_v2}

% Section 4 — Security (PETS-safe)
\input{section4_pets}

\section{Optimality: Lower Bound via Le Cam}

\input{tv_bound_proof}
\input{lower_bound_lecam}
\input{lower_bound}

% Section 6 — Evaluation
\input{section5_evaluation}

% Section 7 — Related Work
\section{Related Work}

Bonawitz et al.~\cite{Bonawitz2017} propose
secure aggregation without DP guarantees.
DP-SGD~\cite{Abadi2016} adds DP to gradient
descent but assumes a single trusted server.
ANCRE v0.8 combines MPC, DP, and irreversible
destruction --- no prior work achieves all three.

% Section 8 — Conclusion
\section{Conclusion}

ANCRE v0.8 provides the first formally optimal
privacy-destruction protocol under H6-MPC.
The optimality result (Le Cam lower bound)
shows that no mechanism can achieve
$\varepsilon$-DP with less noise while
guaranteeing irreversible destruction.

Future work: formal TEE attestation (v0.9),
zero-knowledge proof of destruction,
extension to adaptive corruption model.

\bibliographystyle{plain}
\bibliography{bibliography}

\end{document}
