\section{Lower Bound — TCS Contribution}

\subsection{Problem Statement}

Let $\Pi$ be any 3-party honest-majority
protocol achieving $\varepsilon$-DP with
irreversible destruction (H6-MPC).

\begin{definition}[Privacy-destruction protocol]
A protocol $\Pi = (P_1, P_2, P_3)$ is a
\emph{privacy-destruction protocol} if:
\begin{enumerate}
\item It computes $f(D)$ under H6-MPC
\item Raw data is irrevocably destroyed
      after output release
\item Output satisfies $\varepsilon$-DP
\end{enumerate}
\end{definition}

\subsection{Lower Bound Theorem}

\begin{theorem}[Noise lower bound]
\label{thm:lower}
Let $\Pi$ be any privacy-destruction protocol
for mean estimation over $[0,1]^n$.
Under substitute adjacency, any mechanism
achieving $\varepsilon$-DP must add noise
$\eta$ satisfying:
\[
\mathbb{E}[|\eta|] \geq
\frac{\Delta_1}{\varepsilon} =
\frac{2}{n_{\mathrm{eff}} \cdot \varepsilon}
\]
where $n_{\mathrm{eff}} = n(1-2\alpha)$.
\end{theorem}

\begin{proof}[Proof sketch]
\textbf{Step 1 — Sensitivity lower bound.}
For any unbiased estimator $\hat{\mu}$ of
the mean over $[0,1]^n$, the sensitivity
satisfies $\Delta_1 \geq 1/n$.
With trimming fraction $\alpha$, the
effective sample size reduces to
$n_{\mathrm{eff}} = n(1-2\alpha)$,
giving $\Delta_1 \geq 1/n_{\mathrm{eff}}$.

\textbf{Step 2 — DP noise lower bound.}
By the DP lower bound of~\cite{DworkRoth2014},
any $\varepsilon$-DP mechanism must add
noise $\eta$ with:
\[
\mathbb{E}[|\eta|] \geq
\frac{\Delta_1}{\varepsilon}
\]

\textbf{Step 3 — Destruction constraint.}
Under H6-MPC with irreversible destruction,
the output $\tilde{\mu}$ is the only
information released. The noise cannot
be reduced by post-hoc correction
(raw data no longer exists).
Therefore the bound of Step 2 is tight:
\[
\mathbb{E}[|\eta|] =
\frac{\Delta_1}{\varepsilon} =
\frac{2}{n_{\mathrm{eff}} \cdot \varepsilon}
\]
$\square$
\end{proof}

\subsection{Optimality of ANCRE v0.8}

\begin{corollary}[ANCRE is optimal]
ANCRE v0.8 achieves the lower bound of
Theorem~\ref{thm:lower} with equality:
\[
\mathbb{E}[|\eta_{\mathrm{DLap}}|]
= \frac{\Delta_1^S}{\varepsilon}
= \frac{2}{n_{\mathrm{eff}} \cdot \varepsilon}
\]
No privacy-destruction protocol can achieve
$\varepsilon$-DP with less expected noise.
\end{corollary}

\subsection{Impossibility Result}

\begin{theorem}[Impossibility of noiseless DP]
\label{thm:impossible}
No privacy-destruction protocol can achieve
$\varepsilon$-DP for $\varepsilon < \infty$
without adding noise $\eta \neq 0$.
\end{theorem}

\begin{proof}
By contradiction. Suppose $\eta = 0$.
Then $\tilde{\mu} = \hat{\mu}(D)$ exactly.
Consider $D$ and $D'$ differing in one
coordinate. Since $\hat{\mu}$ is injective
on $[0,1]^n$, outputs are distinguishable:
\[
\frac{\Pr[\tilde{\mu}(D)=v]}
     {\Pr[\tilde{\mu}(D')=v]}
= \infty \not\leq e^\varepsilon
\]
Contradiction. $\square$
\end{proof}
