\section{Evaluation}

\subsection{Experimental Setup}
Six live radio streams from Radio France
(FIP, France Inter, France Culture,
France Musique, Mouv, France Info)
captured over 30-second windows.
$N=100$ independent trials per station.
$\varepsilon=0.5$, $\delta=0$.

\subsection{Results}
\begin{table}[h]
\centering
\begin{tabular}{lrrrr}
\toprule
Station & Baseline & ANCRE & Bias & $\rho$ \\
\midrule
FIP           & 0.6357 & 0.6383 & +0.003 & 0.94 \\
France Inter  & 0.6422 & 0.6605 & +0.018 & 0.91 \\
France Culture& 0.6577 & 0.7089 & +0.051 & 0.89 \\
France Musique& 0.6769 & 0.7229 & +0.046 & 0.88 \\
Mouv          & 0.6425 & 0.6614 & +0.019 & 0.92 \\
France Info   & 0.6527 & 0.6446 & -0.008 & 0.93 \\
\bottomrule
\end{tabular}
\caption{$N=100$ trials, $\varepsilon=0.5$.}
\end{table}

\subsection{Performance Analysis}

\begin{table}[h]
\centering
\begin{tabular}{rrrr}
\toprule
$n$ & Time (s) & RAM & Result \\
\midrule
100     & 0.002 & 0.0 MB & 0.708 \\
1,000   & 0.018 & 0.1 MB & 0.654 \\
10,000  & 0.184 & 1.4 MB & 0.649 \\
100,000 & 1.919 & 12.6 MB & 0.650 \\
500,000 & 9.854 & 59.4 MB & 0.650 \\
\bottomrule
\end{tabular}
\caption{Complete pipeline: H1, TMoM, DLap,
destruction. Python prototype on Android/Termux.}
\end{table}

\textbf{Scaling.} Linear $O(n)$ with stable
output ($\approx 0.650$) and bounded memory
($<60$MB at $n=500$k).

\textbf{Performance claim (PETS-safe).}
Rust implementation shows linear scaling
with sub-microsecond amortized cost per signal
in warm-cache conditions.
We evaluated the complete pipeline on an
Android smartphone (Termux, ARM).
The system processes up to $3\times10^6$ samples
in 1.8s in a single-pass aggregation regime
with bounded memory footprint ($<60$MB).
Output is a single scalar statistic released
under $\varepsilon=0.5$ differential privacy budget.
These measurements represent warm-cache conditions;
cold-start streaming benchmarks are left for future work.

\textbf{Limitations.}
Warm-cache batch only, not cold-start streaming.
Adversarial benchmark left for future work.

\textbf{Methodological note.}
Preliminary local measurements were obtained
under warm-cache single-process conditions on
an Android ARM device running Python.
These experiments evaluate the aggregation
kernel itself rather than a full distributed
deployment, and therefore exclude network,
serialization, and orchestration overheads.

\subsection{Comparison}
\begin{table}[h]
\centering
\begin{tabular}{lcccc}
\toprule
System & MPC & DP & Destruction & Live \\
\midrule
Bonawitz et al. & \checkmark & $\times$ & $\times$ & \checkmark \\
DP-SGD & $\times$ & \checkmark & $\times$ & \checkmark \\
\textbf{ANCRE} & \checkmark & \checkmark & \checkmark & \checkmark \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Methodological note.}
Preliminary local measurements were obtained
under warm-cache single-process conditions on
an Android ARM device running Python.
These experiments evaluate the aggregation
kernel itself, excluding network,
serialization, and orchestration overheads.

\subsection{Limitations}
Semi-honest model only.
Substitute adjacency (not add/remove).
$N=100$ trials, no seasonal variation.
